A Tale of Two Transects

### 2020-01-22 writing/transect_paper.Rmd
change import format for datasets to match new columns

datasets <- read_csv(here("config/datasets.csv"), col_types = "ccccicccccicc")
regions <- read_csv(here("config/regions.csv"), col_types = "cccciiiiic")

@@

## Read counts

@@

(ref:readcounts) Number of Amplicon Sequence Variants (ASV) and reads at different pipeline stages.
Raw: raw reads as delivered by sequencing center;
Trim: reads with primers and demultiplexing indices removed;
LSUx: reads with a positive CM hit for 5.8S, allowing regions to be extracted;
ITS2: ASVs obtained for the ITS2 region, and reads successfully mapped to an ITS2 ASV;
short, ITS, LSU, long: ITS2-based ASVs mapped to consensus ASVs for longer regions, where \"short\" and \"song\" denote the full-length short and long amplicons, respectively.
Short amplicons were mapped to full ITS, LSU, and long amplicon ASVs when

@@

(ref:variofit) Parameters for variogram fits shown in Figure \@ref(fig:spatio-temporal). Range: range at which exponential function is at 95% of its maximum value; Anisotropy: effective spatial distance represented by one year; R/A: Range divided by anisotropy; the characteristic range of the exponential function in the time domain.

```{r variofit}
variog_data %>%
  mutate_at("variofitST", lapply, purrr::compose(as.data.frame, as.list, gstat::extractPar)) %>%
  unnest(variofitST) %>%
  arrange(metric, amplicon, guild) %>%
  select(Guild = guild, Amplicon = amplicon, Metric = metric,
         Range = range, Anisotropy = anis) %>%
  mutate(Range = 3*Range,
         "Time Range" = Range/Anisotropy,
         "R/A" = ifelse(`R/A` > 100, NA, `R/A`)) %>%
  mutate_at(c("Range", "Time Range"), formatC, digits = 1,
            format = "f") %>%
  mutate_at("Range", paste, "m") %>%
  mutate_at("Anisotropy", paste, "m/a") %>%
  mutate_at("R/A", paste, "a") %>%
  mutate_at("R/A", str_replace, "NA a", "-") %>%
  mutate_at("Amplicon", fct_relabel, str_replace, " amplicon", "") %>%
  kable(booktabs = TRUE, caption = "(ref:variofit)")
```

>>>>

datasets <- read_csv(here("config/datasets.csv"), col_types = "cccccccicccccicc")
regions <- read_csv(here("config/regions.csv"), col_types = "cccciiiiic")

@@

## Sequencing

@@

(ref:readcounts) Number of Amplicon Sequence Variants (ASV) and reads at different pipeline stages.
*Raw*: raw reads as delivered by sequencing center;
*Trim*: reads with primers and demultiplexing indices removed;
*LSUx*: reads with a positive CM hit for 5.8S, allowing regions to be extracted;
*ITS2*: ASVs obtained for the ITS2 region, and reads successfully mapped to an ITS2 ASV;
*short*, *ITS*, *LSU*, *long*: ITS2-based ASVs mapped to consensus ASVs for longer regions, where \"short\" and \"long\" denote the full-length short and long amplicons, respectively.
Short amplicons were mapped to full ITS, LSU, and long amplicon ASVs when

@@

(ref:variofit) Parameters for variogram fits shown in Figure \@ref(fig:spatio-temporal). Range: range at which exponential function is at 95% of its maximum value; Anisotropy: effective spatial distance represented by one year; the characteristic range of the exponential function in the time domain.

```{r variofit}
variog_data %>%
  mutate_at("variofitST", lapply, purrr::compose(as.data.frame, as.list, gstat::extractPar)) %>%
  unnest(variofitST) %>%
  arrange(metric, amplicon, guild) %>%
  select(Guild = guild, Amplicon = amplicon, Metric = metric,
         Range = range, Anisotropy = anis) %>%
  mutate(Range = 3*Range,
         "Time Range" = Range/Anisotropy,
         "Time Range" = ifelse(`Time Range` > 100, NA, `Time Range`)) %>%
  mutate_at(c("Range", "Time Range"), formatC, digits = 1,
            format = "f") %>%
  mutate_at("Range", paste, "m") %>%
  mutate_at("Anisotropy", paste, "m/a") %>%
  mutate_at("R/A", paste, "a") %>%
  mutate_at("R/A", str_replace, "NA a", "-") %>%
  mutate_at("Amplicon", fct_relabel, str_replace, " amplicon", "") %>%
  kable(booktabs = TRUE, caption = "(ref:variofit)")
```
